Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-15 writeup/RochatEtal_ResponseToReviewers.tex

We thank reviewer \#1 for the speedy review. Below we address the reviewer’s
comments and suggestions.

\begin{enumerate}

\item {\it In the bottom paragraph on P.10, the authors emphasized that "At scales larger
than 20km, the April and October spectra based on hourly velocity snapshots are
nearly indistinguishable from each other". This emphasis appears to be contradictory
to the statements in other places of the manuscript that the seasonality of subinertial
submesoscale flows is strong (e.g., those relating to Figure 1b-c and Figure 2).}

\item {\it Does the mesoscale eddy variability in the Kuroshio Extension region of the model
have a similar energy level as those in the along-track altimeter data? This point
is worth mentioning as it impacts on the relative importance between the instability-induced
turbulence versus inertia-gravity waves.}

@@

\item {\it P.7, line 12: Change "KE spectra" to "KE spectrum"?}

Fixed.

\item {\it P.8, bottom: The black line in Figure 2c shows a non-zero divergence value.
      Shouldn't the gridded SSH data be non-divergent by definition?}

  The convergence of meridians (the $\beta$-effect) accounts for the
  small divergence depicted by the black line in Figure 2c.

@@

\item {\it (Section 2, Paragraph 1) ``The LLC4320 simulation is an extension of the 3-month
      long output used by Rocha et al. (2016).'' I think this is good to mention, here, so
      please keep. In contrast, in (Section 5, Paragraph 2) the authors note a consistency
      between the results in the Kuroshio Extension and those in the Drake Passage. This is
      not a consistency as it is a different location, different time. The author has already
      made the reader aware of the previous study so there is no reason to cite again.}

\item {\it (Section 5, Paragraph 1) eliminate ``spectral'' after Hanning window. Also, no need for
        quotation marks.}\\
        OK.

\item {\it (Section 5, Paragraph 1) ``the projection of these flows onto different horizontal scales
            ...'' Have you thought about computing scale-dependent vorticity, strain rate and
            divergence? This is really what you would be doing
            aforementioned flows into spectral space.}

\item {\it (Section 5, Paragraph 3) Remove the exclamation mark.}\\

    Removed.

### 2016-08-15 writeup/rocha_etal.tex
Fixes typos.

To better quantify the projection of these flows onto different horizontal
scales, we calculate wavenumber spectra of kinetic energy and sea-surface height
 variance.  Before calculating the spectra, time-mean and spatial linear
trends were removed, and the resulting fields were multiplied by a two-dimensional Hanning ``spectral window''.
The two-dimensional spectra were averaged azimuthaly \citep[e.g., ][]{rocha_etal2016} .
We discuss only spectra for the 1/48$^\circ$ simulation, which extends the 1/24$^\circ$ simulation
towards smaller scales (supporting information).

@@

The inertia-gravity waves project on the sea-surface.
There is a dramatic difference between the spectra
based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig4}b): at scales smaller than 100 km, the spectra
of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October! Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface submesoscale inertia-gravity waves conspire to yield weak seasonality
in the spectra of KE and sea-surface height variance based on hourly fields.

>>>>

To better quantify the projection of these flows onto different horizontal
scales, we calculate wavenumber spectra of kinetic energy and sea-surface height
 variance.  Before calculating the spectra, time-mean and spatial linear
trends were removed, and the resulting fields were multiplied by a two-dimensional Hanning window.
The two-dimensional spectra were averaged azimuthaly \citep[e.g., ][]{rocha_etal2016} .
We discuss only spectra for the 1/48$^\circ$ simulation, which extends the 1/24$^\circ$ simulation
towards smaller scales (supporting information).

@@

The inertia-gravity waves project on the sea-surface.
There is a dramatic difference between the spectra
based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig4}b): at scales smaller than 100 km, the spectra
of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface submesoscale inertia-gravity waves conspire to yield weak seasonality
in the spectra of KE and sea-surface height variance based on hourly fields.
